---
title: "LMwithPred"
author: "Jonathan Clavio"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This is the linear model with prediction problem.  
Predict strength scores using data from the following web site.  

$H_0$: The Null Hypothesis is that there is no difference between arms and grip strength.  

$H_A$: The Alternative Hypothesis is that there is a difference between arms and grip strength for overall strength.


 
```{r}
data <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt", sep="", header=TRUE)
```
 
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
require(ggplot)
```

## Arm

```{r}
plot(SIMS~ARM,data=data)
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
New=data.frame (GRIP=94, ARM=88)
predict.lm(model.1,New,interval="prediction")
```

In the data the arm strength estimate in adjusted R-Squared is 0.467.  


## Grip


```{r}
plot (SIMS~GRIP,data=data)
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```


```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
predict.lm(model.2,New,interval="prediction")
```

The adjusted R-Squared in grip strength is 0.4053.  


```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
predict.lm(model.3,New,interval="prediction")
```


```{r}
anova(model.1,model.3)
```


## Conclusion

The adjusted r-squared for Arm strength is at 0.467 and for grip is at 0.4053. With this data, we therefore reject the Null Hypothesis and accept the Alternative Hypothesis. The guys with the stronger arms in general are better on the physically demanding parts of the job compared to people with high grip strength. 
